Formal Synthesis of Digital Controllers for Observable Continuous Plants with Transient Performance Specifications

### 2018-04-23 CONCUR2018/paper.tex
another nudge

@@

Given the nature of the specifications, observer synthesis cannot be directly compared to full state controller synthesis. 
On average, we found the former to be over an order of magnitude slower for the given benchmarks, largely due to the fact that the introduction of the
observer doubles the order of the model.

>>>>

We note that the introduction of an observer doubles the size of the model w.r.t.
a full state controller, which will have an average polynomial, worst case
exponential time increase in the sysnthesis engine.

@@
